Labeled object representation and manipulation with ITK

### 2007-09-11 article/Article.tex
hum, record the table
darcs-hash:20070911120623-2fc9d-8efb3bdb81b319778c05546ac19c987b3fca824f.gz
add some examples
darcs-hash:20070911160033-2fc9d-d51d9ffc4f04b087135ddeda32880cc6650524e8.gz

@@

@@

@@

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[A label Image.]{\includegraphics[scale=0.7]{cthead1-label2}}
\subfigure[The same image with colored labels]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
\caption{(a) the label image of connected components in Figure~\ref{fig:binaryImage}. (b) is the same image with labels colored with {\em itk::LabelToRGBImageFilter}.\label{fig:labelImage}}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[A simple binary image.]{\includegraphics[scale=0.7]{cthead1-bin}}
\subfigure[A binary image, or a label image?]{\includegraphics[scale=.7]{2th_cthead1}}
\caption{(a) is a simple binary image. Usually, the white pixel have the value 255, and the background the value 0. (b) contains 3 values (0, 100 and 200). The foreground value must be defined by the user, either 0, 100 or 200, and the values which are not the foreground are in the background.\label{fig:binaryImage}}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[A label image]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
\subfigure[All the objects smaller than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-bigger-than-1000}}
\subfigure[All the objects greater than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-smaller-than-1000}}
\subfigure[All the objects with roundness smaller than 0.8 removed]{\includegraphics[scale=.7]{cthead1-label2-roundness-greater-than-0_8}}
\subfigure[All the objects with elongation smaller than 10 removed]{\includegraphics[scale=.7]{cthead1-label2-binaryElongation-greater-than-10}}
\subfigure[All the objects with perimeter smaller than 100 removed]{\includegraphics[scale=.7]{cthead1-label2-perimeter-greater-than-100}}
\caption{Some example of opening with different attribute and parameters.}
\end{center}
\end{figure}

@@

\begin{table}[phtb]
\centering
\small
\begin{tabular}{cccc}
\hline
nucleus	& x	& y	& mean	\\
\hline
1	& 117.925925926	& 146.111111111	& 188.185185185	\\
1	& 154.25	& 87.4166666667	& 126.416666667	\\
1	& 107.666666667	& 155.125	& 122.0	\\
1	& 95.2380952381	& 78.2857142857	& 121.0	\\
2	& 417.631578947	& 158.736842105	& 132.894736842	\\
2	& 431.277777778	& 177.388888889	& 131.222222222	\\
2	& 390.117647059	& 207.588235294	& 96.8235294118	\\
2	& 396.8		& 113.666666667	& 113.2	\\
3	& 251.148148148	& 358.814814815	& 105.037037037	\\
3	& 189.333333333	& 407.888888889	& 111.074074074	\\
3	& 293.72	& 454.8		& 95.48	\\
3	& 239.888888889	& 411.111111111	& 135.222222222	\\
\hline
\hline
\end{tabular}
\caption{Output of the python example.}
\end{table}
